---
title: "Branch Visitor Profile"
date: "07/21/2023"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: united
    number_sections: true
    code_folding: hide
---
<style type="text/css">
.main-container {
  max-width: 100%;
  margin-left: auto;
  margin-right: auto;
}

div.main-container {
  max-width: 100%;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```


```{r}
rm(list=ls())
library(data.table)
library(ggplot2)
library(dplyr)
library(stringr)
library(lfe)
library(stargazer)

data_path = 'C:/Users/dratnadiwakara2/Documents/OneDrive - Louisiana State University/Raw Data/Dewey/'
```


```{r}
poi_sod <- fread(paste0(data_path,"poi_sod.csv.gz"))
poi_sod <- poi_sod[,c("CERT","UNINUMBR","NAMEFULL","usps_address","full_address_poi","LOCATION_NAME","PLACEKEY")]
poi_sod <- poi_sod[usps_address != ""]
poi_sod <- poi_sod[substr(tolower(NAMEFULL),1,2)==substr(tolower(LOCATION_NAME),1,2)]
poi_sod <- poi_sod[!duplicated(poi_sod[,c("PLACEKEY")])]
poi_sod <- poi_sod[!grepl(" ATM", LOCATION_NAME)]
poi_sod_s <- poi_sod[,c("UNINUMBR","PLACEKEY")]
poi_sod_s <- poi_sod_s[!duplicated(poi_sod_s$UNINUMBR)]
```

```{r}
visits_summary <- fread(paste0(data_path,"place_month_visit_summary.csv.gz"))
visits_summary <- visits_summary[PLACEKEY %in% poi_sod$PLACEKEY]
visits_summary <- merge(visits_summary,poi_sod_s,by="PLACEKEY")
```

```{r}
# monthly number of visits from a particular censustract to a given placekey together with censustract demographic characteristics
visits_acs_merged <- fread(paste0(data_path,"visits_acs_merged.gz"))
setkey(visits_acs_merged,PLACEKEY,DATE_RANGE_START)

exclude_cols <- c("PLACEKEY", "DATE_RANGE_START","no_visits","censustract")

place_visitor_wa <- visits_acs_merged[, lapply(.SD, weighted.mean, w = no_visits, na.rm = TRUE), by = .(PLACEKEY, DATE_RANGE_START), .SDcols = setdiff(names(visits_acs_merged), exclude_cols)]

```


```{r}
place_visitor_wa <- place_visitor_wa[PLACEKEY %in% poi_sod$PLACEKEY]
place_visitor_wa <- merge(place_visitor_wa,poi_sod_s,by="PLACEKEY")

place_visitor_wa <- merge(place_visitor_wa,visits_summary[,c("PLACEKEY","DATE_RANGE_START","RAW_VISITOR_COUNTS")],by=c("PLACEKEY","DATE_RANGE_START"))

exclude_cols <- c("PLACEKEY", "DATE_RANGE_START","RAW_VISITOR_COUNTS","UNINUMBR")

avg_visitor <- place_visitor_wa[, lapply(.SD, weighted.mean, w = RAW_VISITOR_COUNTS, na.rm = TRUE),
                                by = UNINUMBR, .SDcols = setdiff(names(place_visitor_wa), exclude_cols)]
```


```{r}
g <- list()
g[[1]] <- ggplot(avg_visitor,aes(x=median_age))+geom_histogram()
g[[2]] <- ggplot(avg_visitor,aes(x=below_poverty_frac))+geom_histogram()
g[[3]] <- ggplot(avg_visitor,aes(x=median_income_last_12_months))+geom_histogram()
g[[4]] <- ggplot(avg_visitor,aes(x=internet_frac))+geom_histogram()
g[[5]] <- ggplot(avg_visitor,aes(x=college_or_higher_frac))+geom_histogram()
g[[6]] <- ggplot(avg_visitor,aes(x=owner_occ_frac))+geom_histogram()

gridExtra::grid.arrange(g[[1]],g[[2]],g[[3]],g[[4]],g[[5]],g[[6]])
```


```{r}
sod_2021 <- fread("C:/Users/dratnadiwakara2/Documents/OneDrive - Louisiana State University/Raw Data/SOD/data/ALL_2022.csv",select = c("UNINUMBR","CERT","RSSDID","ASSET","DEPSUMBR","STCNTYBR","RSSDHCR","ZIPBR"))
sod_2021[,DEPSUMBR:=str_remove_all(DEPSUMBR,",")]
sod_2021[,DEPSUMBR:=as.numeric(DEPSUMBR)]
sod_2021 <- sod_2021[DEPSUMBR>quantile(sod_2021$DEPSUMBR,0.05)]

sod_2022 <- fread("C:/Users/dratnadiwakara2/Documents/OneDrive - Louisiana State University/Raw Data/SOD/data/ALL_2023.csv",select = c("UNINUMBR","DEPSUMBR"))
sod_2022[,DEPSUMBR:=str_remove_all(DEPSUMBR,",")]
sod_2022[,DEPSUMBR:=as.numeric(DEPSUMBR)]
setnames(sod_2022,"DEPSUMBR","DEPSUMBR22")


sod_2022 <- merge(sod_2022,sod_2021,by="UNINUMBR")
sod_2022[,dep_chg:=DEPSUMBR22/DEPSUMBR-1]
sod_2022 <- sod_2022[dep_chg<quantile(sod_2022$dep_chg,0.99) & dep_chg>quantile(sod_2022$dep_chg,0.01)]
```

```{r}
ggplot(sod_2022,aes(x=dep_chg))+geom_histogram()
```


```{r}
sod_acs <- merge(sod_2022,avg_visitor,by="UNINUMBR")
sod_acs[,dep_chg_bin:=ntile(dep_chg,10)]
sod_acs[,ASSET:=str_remove_all(ASSET,",")]
sod_acs[,ASSET:=as.numeric(ASSET)]
```


g[[1]] <- ggplot(avg_visitor,aes(x=median_age))+geom_histogram()
g[[2]] <- ggplot(avg_visitor,aes(x=below_poverty_frac))+geom_histogram()
g[[3]] <- ggplot(avg_visitor,aes(x=median_income_last_12_months))+geom_histogram()
g[[4]] <- ggplot(avg_visitor,aes(x=internet_frac))+geom_histogram()
g[[5]] <- ggplot(avg_visitor,aes(x=college_or_higher_frac))+geom_histogram()
g[[6]] <- ggplot(avg_visitor,aes(x=owner_occ_frac))+geom_histogram()



```{r}
r <- list()
r[[1]] <- felm(log(1+dep_chg)~log(median_age)|CERT,data=sod_acs)
r[[2]] <- felm(log(1+dep_chg)~log(median_income_last_12_months)|CERT,data=sod_acs)
r[[3]] <- felm(log(1+dep_chg)~internet_frac|CERT,data=sod_acs)
r[[4]] <- felm(log(1+dep_chg)~college_or_higher_frac|CERT,data=sod_acs)
r[[5]] <- felm(log(1+dep_chg)~owner_occ_frac|CERT,data=sod_acs)
r[[6]] <- felm(log(1+dep_chg)~log(median_age)+log(median_income_last_12_months)+internet_frac+college_or_higher_frac+owner_occ_frac+owner_occ_frac|CERT,data=sod_acs)
stargazer(r,type="text",omit.stat = "ser")
```


```{r}
r <- list()

r[[1]] <- felm(log(1+dep_chg)~log(median_age)+log(ASSET)|STCNTYBR,data=sod_acs)
r[[2]] <- felm(log(1+dep_chg)~log(median_income_last_12_months)+log(ASSET)|STCNTYBR,data=sod_acs)
r[[3]] <- felm(log(1+dep_chg)~internet_frac+log(ASSET)|STCNTYBR,data=sod_acs)
r[[4]] <- felm(log(1+dep_chg)~college_or_higher_frac+log(ASSET)|STCNTYBR,data=sod_acs)
r[[5]] <- felm(log(1+dep_chg)~owner_occ_frac+log(ASSET)|STCNTYBR,data=sod_acs)
r[[6]] <- felm(log(1+dep_chg)~log(median_age)+log(median_income_last_12_months)+internet_frac+college_or_higher_frac+owner_occ_frac+owner_occ_frac+log(ASSET)|STCNTYBR,data=sod_acs)

stargazer(r,type="text",omit.stat = "ser")
```


```{r}
r <- list()

r[[1]] <- felm(log(median_age)~log(ASSET)|STCNTYBR,data=sod_acs)
r[[2]] <- felm(log(median_income_last_12_months)~log(ASSET)|STCNTYBR,data=sod_acs)
r[[3]] <- felm(internet_frac~log(ASSET)|STCNTYBR,data=sod_acs)
r[[4]] <- felm(college_or_higher_frac~log(ASSET)|STCNTYBR,data=sod_acs)
r[[5]] <- felm(owner_occ_frac~log(ASSET)|STCNTYBR,data=sod_acs)

stargazer(r,type="text",omit.stat = "ser")
```


```{r}
r <- list()

r[[1]] <- felm(log(median_age)~I(ASSET>1e6)|STCNTYBR,data=sod_acs[ASSET<1e7])
r[[2]] <- felm(log(median_income_last_12_months)~I(ASSET>1e6)|STCNTYBR,data=sod_acs[ASSET<1e7])
r[[3]] <- felm(internet_frac~I(ASSET>1e6)|STCNTYBR,data=sod_acs[ASSET<1e7])
r[[4]] <- felm(college_or_higher_frac~I(ASSET>1e6)|STCNTYBR,data=sod_acs[ASSET<1e7])
r[[5]] <- felm(owner_occ_frac~I(ASSET>1e6)|STCNTYBR,data=sod_acs[ASSET<1e7])

stargazer(r,type="text",omit.stat = "ser")
```


```{r}
r <- list()

r[[1]] <- felm(log(median_age)~I(ASSET>1e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[2]] <- felm(log(median_income_last_12_months)~I(ASSET>1e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[3]] <- felm(internet_frac~I(ASSET>1e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[4]] <- felm(college_or_higher_frac~I(ASSET>1e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[5]] <- felm(owner_occ_frac~I(ASSET>1e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e6])

stargazer(r,type="text",omit.stat = "ser")
```


```{r}
r <- list()

r[[1]] <- felm(log(median_age)~I(ASSET>5e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[2]] <- felm(log(median_income_last_12_months)~I(ASSET>5e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[3]] <- felm(internet_frac~I(ASSET>5e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[4]] <- felm(college_or_higher_frac~I(ASSET>5e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[5]] <- felm(owner_occ_frac~I(ASSET>5e7)|STCNTYBR|0|STCNTYBR,data=sod_acs[ASSET>1e7])

stargazer(r,type="text",omit.stat = "ser")
```


```{r}
r <- list()
r[[1]] <- felm(I(ASSET>1e6)~wa_median_age|STCNTYBR,data=sod_acs)
r[[2]] <- felm(I(ASSET>1e6)~wa_below_poverty_frac|STCNTYBR,data=sod_acs)
r[[3]] <- felm(I(ASSET>1e6)~wa_internet_frac|STCNTYBR,data=sod_acs)
r[[4]] <- felm(I(ASSET>1e6)~wa_spanish_speaking_frac|STCNTYBR,data=sod_acs)
r[[5]] <- felm(I(ASSET>1e6)~wa_median_age+wa_below_poverty_frac+wa_internet_frac+wa_white_fraction|STCNTYBR,data=sod_acs)

stargazer(r,type="text")
```

```{r}
r <- list()
r[[1]] <- felm(I(ASSET>1e7)~wa_median_age|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[2]] <- felm(I(ASSET>1e7)~wa_below_poverty_frac|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[3]] <- felm(I(ASSET>1e7)~wa_internet_frac|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[4]] <- felm(I(ASSET>1e7)~wa_spanish_speaking_frac|STCNTYBR,data=sod_acs[ASSET>1e6])
r[[5]] <- felm(I(ASSET>1e7)~wa_median_age+wa_below_poverty_frac+wa_internet_frac+wa_white_fraction|STCNTYBR,data=sod_acs[ASSET>1e6])

stargazer(r,type="text")
```

```{r}
r <- list()
r[[1]] <- felm(I(ASSET>25e7)~wa_median_age|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[2]] <- felm(I(ASSET>25e7)~wa_below_poverty_frac|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[3]] <- felm(I(ASSET>25e7)~wa_internet_frac|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[4]] <- felm(I(ASSET>25e7)~wa_spanish_speaking_frac|STCNTYBR,data=sod_acs[ASSET>1e7])
r[[5]] <- felm(I(ASSET>25e7)~wa_median_age+wa_below_poverty_frac+wa_internet_frac+wa_white_fraction|STCNTYBR,data=sod_acs[ASSET>1e7])

stargazer(r,type="text")
```

```{r}
r <- list()
r[[1]] <- felm(log(1+dep_chg)~wa_median_age+log(ASSET)|STCNTYBR,data=sod_acs)
r[[2]] <- felm(log(1+dep_chg)~wa_below_poverty_frac+log(ASSET)|STCNTYBR,data=sod_acs)
r[[3]] <- felm(log(1+dep_chg)~wa_internet_frac+log(ASSET)|STCNTYBR,data=sod_acs)
r[[4]] <- felm(log(1+dep_chg)~wa_spanish_speaking_frac+log(ASSET)|STCNTYBR,data=sod_acs)
r[[5]] <- felm(log(1+dep_chg)~wa_median_age+wa_below_poverty_frac+wa_internet_frac+wa_white_fraction+log(ASSET)|STCNTYBR,data=sod_acs)

stargazer(r,type="text")
```


```{r}
library(GGally)

Scatter_Matrix <- ggpairs(sod_acs,columns = c(9:22),title = "", axisLabels = "show")

ggsave("scatter plot matrix.png", Scatter_Matrix, width = 7, height = 7, units = "in") 
```


```{r}
ft_raw <- fread(paste0(data_path,"filtered_ft_data.csv.gz"))
```


r[[2]] <- felm(log(1+dep_chg)~wa_below_poverty_frac|STCNTYBR,data=sod_acs)